---
title: "Task1"
author: "Oleksandr Polishchuk"
date: "10/01/2024"
format:
  html:
    embed-resources: true
editor: source
---

## Question 1 

Question description

```{r}
# code for solving task
# Character
char_var <- "Hello, World!"

# Numeric
num_var <- 3.14

# Integer
int_var <- 42L  # The 'L' indicates that this is an integer

# Complex
comp_var <- 2 + 3i  # 'i' denotes the imaginary unit

# Logical
log_var <- TRUE  # Can also be FALSE

# Print the variables
print(char_var)
print(num_var)
print(int_var)
print(comp_var)
print(log_var)

```


## Question 2

Question description Create the next vectors: *sequence from 5 to 75; * numbers: 3.14, 2.71, 0, 13; * with 100 TRUE values.

```{r}
# code for solving task
# Sequence from 5 to 75
seq_var <- 5:75

# Numbers vector
num_vector <- c(3.14, 2.71, 0, 13)

# Vector with 100 TRUE values
true_vector <- rep(TRUE, 100)

# Print the vectors
print(seq_var)
print(num_vector)
print(true_vector)

```


## Question 3 

Question description Create the next matrix:

```{r}
# code for solving task
# Create a matrix
matrix_var <- matrix(c(12, 34, 87, 
                        -12, -12.1, 0, 
                        3.6, 0.5, 1.3), 
                      nrow = 3, byrow = TRUE)

# Print the matrix
print(matrix_var)

```
## Question 4

Question description
4. Create a 'list' with all atomic times.

```{r}
# code for solving task
# Create a list
list_var <- list(character = char_var, 
                  numeric = num_var, 
                  integer = int_var, 
                  complex = comp_var, 
                  logical = log_var)

# Print the list
print(list_var)

  
```

## Question 5

Question description
Create a 'factor' with 3 levels: 'infant' , 'child' , 'adult'.

```{r}
# code for solving task
# Create a factor
factor_var <- factor(c("infant", "child", "adult"), levels = c("infant", "child", "adult"))

# Print the factor
print(factor_var)

```

## Question 6

Question description
Create a 'data frame'

```{r}
# Create a data frame
data_frame_var <- data.frame(
  Name = c("Alice", "Bob", "Charlie"),
  Age = c(5, 10, 20),
  Score = c(95.5, 88.0, 76.5)
)

# Print the data frame
print(data_frame_var)

```

## Question 7

Question description
Change column names of the 'data frame'

```{r}
# Change column names
colnames(data_frame_var) <- c("Student_Name", "Student_Age", "Student_Score")

# Print the updated data frame
print(data_frame_var)

```




